Supplementary Materials for: Empowering the use of community driven preprints in ecology and evolution

### 2024-04-01 supp/supp.qmd
Adding gender plot and quick summary

# Merge with main data frame
#unique(data_genders$name)
data_genders <- rename(data_genders, submitting_author_firstname = name)
data3 <- left_join(data2, data_genders, by = c("submitting_author_firstname"))
#names(data3)
table(is.na(data3$proportion_male)) #157 missing

@@

@@

>>>>

# Merge with main data frame
#unique(data_genders$name)
#data_genders <- rename(data_genders, submitting_author_firstname = name)
data3 <- left_join(data2, data_genders, by = c("submitting_author_firstname"))
#names(data3)
table(is.na(data3$proportion_male)) #157 missing

@@

# Plot the data
data4 %>% filter(!is.na(gender))  %>% ggplot2::ggplot(aes(x = gender)) + geom_bar()

@@

Overall, females were less likely to publish preprints on *EcoEvoRxiv* compared to males (females: `r (table(data4$gender)[1] / sum(table(data4$gender))*100)`% compared to males: `r (table(data4$gender)[2] / sum(table(data4$gender))*100)`%), which is likely a reflection of the broader publishing disparities between male and feamle scientists.
